\section{Introduction}
\addcontentsline{toc}{chapter}{Introduction}


% Set page numbering to arabic the first time we commence a chapter.
% This is required to get the page numbering correct.
\pagenumbering{arabic}
\doublespace{}

This exegesis explores a range of extended techniques that utilise the harmonic series and assess how they can be used in my, and other people's, creative practice. 
These techniques are \underline{\textcolor{blue}{\href{https://vimeo.com/81380931}{multiphonics}}}, \underline{\textcolor{blue}{\href{https://vimeo.com/57219720}{subharmonics}}}, and \underline{\textcolor{blue}{\href{https://vimeo.com/92221539}{half-harmonics}}}, confined to string based instruments due to the scope of this exegesis.\footnote{These video examples are part of Ellen Fallowfield's CelloMap project. I chose to use them as they are pre-existing examples performed by the same professional musician, on the same instrument, in a professional studio, which helps to establish a baseline of what can be expected of the techniques.}
For the purposes of brevity, these harmonic-based extended techniques will simply be referred to as `techniques' throughout the paper, except for when differentiation between standard techniques is needed.

While some techniques such as harmonics are well established and understood, the techniques inside the scope of this exegesis are still underdeveloped in terms of both repertoire and resources available. 
The timbral potentials of these techniques are uncharted territories and collectively represent an entire sound world that remains relatively inaccessible to composers.
My interest lies in the non-binary nature of them; all three techniques have different factors that lead to their production, and can vary greatly in timbre. 
Understanding their attributes will add the techniques to the composer's `toolbox', and contribute to the development of art music.
% TODO: Evidence for uncharted territories - https://trello.com/c/u605dDsM/15-evidence-for-uncharted-territories
% 
% To identify where further research is required, I will conduct a review of the literature and resources that are readily available to composers to assess what techniques require further investigation and refinement. 
% By researching these techniques and the mechanics behind them, interviewing professionals, and analysing recordings made, I hope to gain a better understanding of how these techniques can be implemented in my practice. 
% As part of both the analysis of techniques and my compositional practice, I will assess not only the compositional potential, but also the practicality of techniques. 
% Reviewing the feasibility and notational aspects of the techniques will render the exegesis a practical document to reference for performance and composition.


% I aim for my resulting exegesis to become a useful reference source for artists interested in learning about the mechanics, qualities, and potential implementations of these harmonic based extended techniques. 
% The works that I compose accompanying the exegesis will show idiomatic treatment of the techniques and serve as references as such in the exegesis.

% The dissemination of the material I research will contribute to the accessibility of new sound possibilities for artists.

% what they are
% what the field
% Why i'm interested
% Why I want to do it
% Why its relevant
% To integrate it into the field and wheelhouse

